---
title: "Conflict Dataset"
author: "Tomasz Stąpor"
date: "29 September 2014"
output:
  html_document:
    theme: readable
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=TRUE)
```
```{r echo=FALSE}
load("data/124920_1ucdpprioarmedconflictdataset4.2014.rdata") # import DB doucdpConflict
# http://stackoverflow.com/questions/6081439/changing-column-names-of-a-data-frame-in-r?answertab=votes#tab-top
colnames(ucdpConflict)[1]  <- "ID"
colnames(ucdpConflict)[11] <- "Level"
colnames(ucdpConflict)[15]  <- "Prec"
colnames(ucdpConflict)[17]  <- "Prec2"
```
### 3.14 Startdate

The date of the first battle-related death recorded in the conflict is coded as the Startdate in the dataset. The date is set after the conflict fulfils all criteria required in the definition of an armed conflict, except for the number of deaths. In some cases, the initial fatality occurs in a year prior to the first year of activity. For instance, in the conflict in Ethiopia over the territory Eritrea (conflict ID 78), the first battle-related deaths occurred in September 1961. During the remaining months of 1961, the conflict did not reach the required 25 battle- related deaths threshold and the conflict is thus coded as inactive in 1961. 25 battle-related deaths were not recorded until three years later.9

```{r}
data  <- ucdpConflict[,c(1,2,10,11,14,15,16,17)] # wybór określonych kolumn
head(subset(data, ID=="1-78"))
```
### 3.16 Startdate2

With Version 4-2008 of the dataset, the coding of Startdate2 was changed. Whereas it used to give information on the first time the conflict reached 25 battle-related deaths in one calendar year, thus indicating the date that the conflict fulfilled all criteria required in the definition of an armed conflict for the first time, it now gives the date, as precise as possible, when a given episode of conflict activity reached 25 battle-related deaths. Thus, for each episode of a conflict, a new Startdate2 is coded. In case precise information is lacking, Startdate2 is by default set to 31 December.
An episode is defined as continuous conflict activity. Consequently, a new episode is coded whenever a conflict restarts after one or more year(s) of inactivity. The introduction of episodes within conflicts enables users to distinguish between different phases in the conflict and, potentially, code these as separate conflicts.